---
title: "Script to download data of NDVI"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 July"
output:  
  md_document:
    variant: markdown_github
---
  
  
```{r wd, echo=FALSE}
#---------------------------------
machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/modis_iv', sep='')
#---------------------------------
```

## Packages 
```{r packages, warning=FALSE}
library("rgdal")
library("RCurl")
library("MODIS")
library("MODISTools")
```

# Read spatial info for centroids of Pyrenean oaks 
* id = 142799;  year = 2000; evi= 4.5445; lng = -3.2653977048134; lat = 37.1964115002029 

142801,2001,6.099,0,"annual",-3.26016693812872,37.1964115002029,1


```{r}
mydf <- data.frame(id=c(142799,142801),
          lat=c(37.1964115002029, 37.1964115002029),
          long=c(-3.2653977048134, -3.26016693812872)) 

# Add dates 
mydf$star.date <- rep(2000, nrow(mydf))
mydf$end.date <- rep(2001, nrow(mydf))


GetBands(Product = "MOD13Q1")
GetDates(Product = "MOD13Q1", Lat = mydf$lat[1], Long = mydf$long[1])

MODISSubsets(LoadDat = mydf, Products = "MOD13Q1",
             Bands = "250m_16_days_EVI",
             Size = c(0,0))

subset.string <- read.csv(list.files(pattern = ".asc")[1], 
                          header = FALSE, as.is = TRUE)

subset.string[1, ]


MODISSummaries(LoadDat = mydf, Product = "MOD13Q1", Bands = "250m_16_days_EVI", ScaleFactor = 0.0001)


MODISGrid(NoDataValues = list("MOD13Q1" = c("250m_16_days_EVI" = -3000)))

#### Specify the options for MODIS package: 

* Paths where downloaded files are stored: 
 * `localArcPath`: `/Users/ajpelu/iv_modis` 
 * `outDirPath`: `/Users/ajpelu/iv_modis` 

```{r MODISoptions} 
path_descarga <- "/Users/ajpelu/iv_modis"

MODISoptions(localArcPath = path_descarga,
             outDirPath = path_descarga)
```

## MODIS product options and paths
```{r}
viname <- "ndvi"
product <- "MOD13Q1"
ofilename <- paste0(product, "_", viname, "_brick.grd")

pth <- paste0(path_descarga, "/raster_data/", product)
fileout <- paste(pth, "/", ofilename, sep="")



# function to create directories
if ( !file.exists(fileout)) { 
  if (!file.exists(pth)){ 
    print("the outfolder does not exist and will be created")
    print(pth)
    dir.create(pth)
  }
}


### info about MODIS tile

tileH <- 17
tileV <- 5
begin <- "2002.01.01"
end <- "2002.01.31"

modis.hdf <- getHdf(product= product,
                    begin = begin,
                    end = end,
                    tileH = tileH,
                    tileV = tileV,
                    checkIntegrity = TRUE)
  