---
title: "Test Validation of MODIS data"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 August"
output:  
  md_document:
    variant: markdown_github
---

# Test Validation 
Test for validation for the downloaded data using [`MODISTool` R package](https://cran.r-project.org/web/packages/MODISTools/index.html) and data coming from [Sierra Nevada Global Change Observatory](https://obsnev.es) 

## Prepare data 
```{r wd}
#---------------------------------
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/modis_iv', sep='')
#---------------------------------
```

```{r packages, warning=FALSE, message=FALSE}
library("dplyr")
library("lubridate")
library("printr") # To install see https://github.com/yihui/printr
library("ggplot2")
library("ggthemes")
```

```{r, readData}
## obsnev_data 
obsnev <- read.csv(file=paste0(di,"/data/iv_obsnev.csv"), header=TRUE, sep=",")

## Downloade data with MODISTool 
md <- read.csv(file=paste0(di,"/data/iv_raw_2015.csv"), header=TRUE, sep=",")
```

## Exploring data 
```{r}
head(obsnev)
```

```{r}
head(md)
```

## Test 
Get all the data for a pixel (e.g. `142799`) in a year (e.g. `2000`)

```{r}
myid <- 142799 
myyear <- 2010 
```

```{r}
obsnev %>% 
  filter(iv_malla_modi_id == myid) %>%
  filter(
    year(ymd(fecha)) == myyear) %>% 
  arrange(composite_day_year) %>% 
  select(iv_malla_modi_id, fecha, composite_day_year, evi, ndvi)

md %>%
  filter(id_pixel == myid) %>%
  filter(year %in% myyear) %>% 
  select(id_pixel, date, composite_day_of_the_year, evi, ndvi)
```


## Exploring temporal series of both datasets

```{r, eval=FALSE}
## Exploring two temporal series 
# Preparing data 

aux_md <- md %>%
  mutate(composite_day_year = composite_day_of_the_year,
         iv_malla_modi_id = id_pixel, 
         fecha = as.Date(date), 
         ndvi = ndvi*0.0001,
         evi = evi*0.0001, 
         dataset = 'MTr_package') %>% 
  select(iv_malla_modi_id, fecha, composite_day_year, evi, ndvi, dataset)

aux_obsnev <- obsnev %>% 
  mutate(fecha = as.Date(fecha), 
         ndvi = ndvi*0.0001,
         evi = evi*0.0001,
         dataset = 'obsnev') %>% 
  select(iv_malla_modi_id, fecha, composite_day_year, evi, ndvi, dataset)

aux_df <- rbind(aux_obsnev, aux_md) %>%
  mutate(fecha=as.Date(fecha))


# Export aux dataframe
write.csv(aux_df, file=paste(di, "/data/aux_comparison.csv", sep=""), row.names = FALSE)
# ---
```

See this [shinyapp](https://ajpelu.shinyapps.io/plot_validation/) with interactive plots to compare the both dataset for EVI and NDVI variables. You can also see an example (three pixels) below: 

```{r}
myids <- sample(md$id_pixel, 3)

aux_md <- md %>%
  filter(id_pixel %in% myids) %>%
  mutate(composite_day_year = composite_day_of_the_year,
         iv_malla_modi_id = id_pixel,
         fecha = date,
         dataset = 'MTr_package') %>% 
  select(iv_malla_modi_id, fecha, composite_day_year, evi, ndvi, dataset)

aux_obsnev <- obsnev %>% 
  filter(iv_malla_modi_id %in% myids) %>%
  mutate(dataset = 'obsnev') %>% 
  select(iv_malla_modi_id, fecha, composite_day_year, evi, ndvi, dataset)

aux <- rbind(aux_md, aux_obsnev)


ggplot(aux, aes(as.Date(fecha), y=ndvi*0.0001, colour=dataset)) +
  geom_line(size=1.1) + 
  xlab('date') + ylab('ndvi') + 
  facet_wrap(~iv_malla_modi_id, ncol=1) +
  theme_few() + scale_colour_fivethirtyeight() 
```


